Concurrent Programming with Harmony

### 2020-07-24 book/paper.tex
Fixes bug

{\small
\begin{tabular}{|l|l|}
\hline
\texttt{$e$ == $e$}, \texttt{$e$ != $e$} & two Harmony values of the same type \\
\hline
\texttt{$e$ < $e$, $e$ <= $e$} & any two Harmony values \\
\hline
\texttt{$e$ > $e$, $e$ >= $e$} & any two Harmony values \\
\hline
\texttt{$e$ and $e$ and ...} & two or more booleans \\
\hline
\texttt{$e$ or $e$ or ...} & two or more booleans \\
\hline
\texttt{not $e$} & a boolean \\
\hline
\texttt{-$e$, \string~$e$} & an integer \\
\hline
\texttt{$e$ + $e$ + ...} & two or more integers, tuples, or lists \\
\hline
\texttt{$e$ - $e$} & two integers or sets \\
\hline
\texttt{$e$ * $e$ * ...} & two or more integers \\
\hline
\texttt{$e$ \& $e$ \& * ...} & two or more integers or sets \\
\hline
\texttt{$e$ | $e$ | * ...} & two or more integers or sets \\
\hline
\texttt{$e$ \string^ $e$ \string^ * ...} & two or more integers or sets \\
\hline
\texttt{$e$ / $e$, $e$ // $e$} & two integers (integer division) \\
\hline
\texttt{$e$ \% $e$, $e$ mod $e$} & two integers (division remainder) \\
\hline
\texttt{$e$ ** $e$, $e << e$, $e >> e$} & two integers \\
\hline
\texttt{$\{ e..e \}$} & two integers \\
\hline
\texttt{$e$ [not] in $e$} & first is any Harmony value, second is set \\
\hline
\texttt{$e$ if $e$ else $e$} & middle $e$ must be a boolean \\
\hline
\texttt{!{}$e$} & an address \\
\hline
\texttt{choose $e$} & a set \\
\hline
\texttt{min $e$, max $e$} & a set \\
\hline
\texttt{cardinality $e$} & a set \\
\hline
\texttt{keys $e$, len $e$} & a dictionary (includes tuple or list) \\
\hline
\texttt{bagsize $e$} & a bag \\
\hline
\texttt{atLabel $e$} & atom (corresponding to a label) \\
\hline
\texttt{nametag $e$} & $e$ must be \texttt{()} \\
\hline
\texttt{processes $e$} & $e$ must be \texttt{()} \\
\hline
\texttt{setintlevel} \textit{e} & \textit{e} is a boolean \\
\hline
\texttt{stop} \textit{lv} & \textit{lv} is an lvalue \\
\hline
\texttt{?}\textit{lv} & \textit{lv} is an lvalue \\
\hline
\end{tabular}
}
\vspace{1em}

>>>>

{\small
\begin{tabular}{|l|l|}
\hline
\texttt{$e$ == $e$}, \texttt{$e$ != $e$} & two Harmony values of the same type \\
\hline
\texttt{$e$ < $e$, $e$ <= $e$} & any two Harmony values \\
\hline
\texttt{$e$ > $e$, $e$ >= $e$} & any two Harmony values \\
\hline
\texttt{$e$ and $e$ and ...} & two or more booleans \\
\hline
\texttt{$e$ or $e$ or ...} & two or more booleans \\
\hline
\texttt{not $e$} & a boolean \\
\hline
\texttt{-$e$, \string~$e$} & an integer \\
\hline
\texttt{$e$ + $e$ + ...} & two or more integers, tuples, or lists \\
\hline
\texttt{$e$ * $e$ * ...} & two or more integers \\
\hline
\texttt{$e$ - $e$} & two integers or sets \\
\hline
\texttt{$e$ \& $e$ \& ...} & two or more integers or sets \\
\hline
\texttt{$e$ | $e$ | ...} & two or more integers or sets \\
\hline
\texttt{$e$ \string^ $e$ \string^ ...} & two or more integers or sets \\
\hline
\texttt{$e$ / $e$, $e$ // $e$} & two integers (integer division) \\
\hline
\texttt{$e$ \% $e$, $e$ mod $e$} & two integers (division remainder) \\
\hline
\texttt{$e$ ** $e$, $e << e$, $e >> e$} & two integers \\
\hline
\texttt{$\{ e..e \}$} & two integers \\
\hline
\texttt{$e$ [not] in $e$} & first is any Harmony value, second is set \\
\hline
\texttt{$e$ if $e$ else $e$} & middle $e$ must be a boolean \\
\hline
\texttt{!{}$e$} & an address \\
\hline
\texttt{choose $e$} & a set \\
\hline
\texttt{min $e$, max $e$} & a set \\
\hline
\texttt{cardinality $e$} & a set \\
\hline
\texttt{keys $e$, len $e$} & a dictionary (includes tuple or list) \\
\hline
\texttt{bagsize $e$} & a bag \\
\hline
\texttt{atLabel $e$} & atom (corresponding to a label) \\
\hline
\texttt{nametag $e$} & $e$ must be \texttt{()} \\
\hline
\texttt{processes $e$} & $e$ must be \texttt{()} \\
\hline
\texttt{setintlevel} \textit{e} & \textit{e} is a boolean \\
\hline
\texttt{stop} \textit{lv} & \textit{lv} is an lvalue \\
\hline
\texttt{?}\textit{lv} & \textit{lv} is an lvalue \\
\hline
\end{tabular}
}
\vspace{1em}
